Data Exploration: IUCN and AquaMaps

### 2015-09-08 data_explore.Rmd
Fixed plot titles...

``` {r pct overlap vs area, echo = FALSE}

@@

# remove all area greater than 100000000

@@

# Log transform area

logA_vs_pct <- ggplot(spp_list, aes(log_total_area, sm_perc, color = sm_range)) + 
  geom_point() + 
  labs(x = 'Total Area (km2)', y = 'Percent overlap smaller range in larger', 
       title = 'Size of species range vs. percent overlap of \nsmaller range with larger')

@@

``` {r examine quartiles, echo = FALSE}

@@

  qtile_plot <- ggplot(area_clip, aes(total_area, sm_perc, color = sm_range)) + 
  geom_point() + 
  labs(x = 'Total Area (km2)', y = 'Percent overlap smaller range in larger', 
       title = 'Size of species range vs. percent overlap of \nsmaller range with larger')

>>>>

Exploring possible correlation between area and percent coverage:
``` {r pct overlap vs area, echo = FALSE}

@@

Perent coverage as function of area, clipping to area below 100,000,000 km^2:
``` {r, echo = F}
# remove all area greater than 100000000

@@

Percent coverage as a function of log(area)
``` {r, echo = F}
# Log transform area

logA_vs_pct <- ggplot(spp_list, aes(log_total_area, sm_perc, color = sm_range)) + 
  geom_point() + 
  labs(x = 'Log(total Area)', y = 'Percent overlap smaller range in larger', 
       title = 'Size of species range (log) vs. percent overlap of \nsmaller range with larger')

@@

Examining data broken into quartiles to see if smaller patterns emerge
``` {r examine quartiles, echo = FALSE}

@@

  qtile_plot <- ggplot(area_clip, aes(total_area, sm_perc, color = sm_range)) + 
  geom_point() + 
  labs(x = 'Total Area (km2)', y = 'Percent overlap smaller range in larger', 
       title = sprintf('Size of species range (quartile %s) vs. percent overlap of \nsmaller range with larger', i))
